Finding Optimal Sequences for Area Aggregation---\protect\\ \Astar vs. Integer Linear Programming

### 2019-04-21 area_agg_seq_tsas.tex
improved our paper while writing review response

\fancyhead[LO]{Finding Optimal Sequences for Area Aggregation}

\begin{document}
\title{Finding Optimal Sequences for Area Aggregation---\protect\\ 
	\Astar vs. Integer Linear Programming
    }
%\titlenote{Produces the permission block, and
%  copyright information}
%\subtitle{Extended Abstract}
%\subtitlenote{The full version of the author's guide is available as
%  \texttt{acmart.pdf} document}

@@

In our digital age, people interactively read maps 
on computers and mobile phones.
An often used interaction is zooming. 
When users zoom in or out, 
a map must be changed to provide information 
appropriate to the corresponding zoom level.
However, large discrete changes may distract users.
The \emph{on-the-fly generalization}~\parencite{Weibel2017Fly},
which generalizes features in real time, can mitigate this problem.
Still, large discrete changes can be introduced.
By a usability test, \textcite{Midtbo2007} have shown that 
a map is easier to follow 
if the map extent transits smoothly than stepwise. 
In addition to smoothly transiting map extent, 
we want to change also map features smoothly 
when users are zooming.
we believe that this strategy will allow users 
to follow maps even more easily.
The process of producing maps at any different scales
with smooth changes 
is known as \emph{continuous map generalization} (CMG), 
or simply \emph{continuous generalization}.
Ideally, there should be no discrete change in CMG.
However, the term is also used when 
the discrete changes are small enough not to be noticed as,
e.g., \textcite{Suba2016Road} state.
We believe that digital maps will eventually 
achieve smooth changes for zooming,
and CMG is an effective way to realize smooth changes.

\mypar{Problem definition}
In this paper, we deal with CMG of land-cover areas.
The land-cover area is of significant importance on maps.
When users zoom out, some land-cover areas become
too tiny to be seen, which result in visual clutter.
In order to provide users 
with good visual experience during zooming operations,
we propose to remove these tiny areas.
We plan to achieve this goal by 
aggregating them into neighboring land-cover areas.
A \emph{land-cover map} is a planar subdivision in which 
each area belongs to a land-cover class or \emph{type}.
Suppose that there are two land-cover maps of different scales 
that cover the same spatial region.
We consider the problem of finding a sequence 
of small incremental changes that gradually transforms 
the larger-scale map (the \emph{start map}) to 
the smaller-scale map (the \emph{goal map}).
We use this sequence to generate and show land-cover maps at 
intermediate scales (see \fig\ref{fig:AreaAgg_example}).
In this way, we try to avoid large and discrete changes
during zooming.

@@

We assume that there exist many-to-one relationships 
between the areas of the start map and the areas of the goal map.
This assumption is based on the fact that many algorithms 
\parencite[e.g.,][]{HaunertWolff2010AreaAgg,
vanSmaalen2003,Oehrlein2017Aggregation}
result in many-to-one relationships
when aggregating land-cover areas.
Their inputs and generalized results together
can be used as our inputs.
However, we should not use those algorithms
to generate a sequence of maps at different scales
because those algorithms do not take into account 
the consistence of the generated maps.
We term the areas of the goal map \emph{regions}.
That is, every region is the union of a set of areas 
on the start map.
The type of a region may differ from the types of its components. 
For example, a small water area together with 
multiple adjacent forest areas may constitute 
a large forest region on the smaller-scale map.
However, we assume that every region, on the goal map, 
contains at least one area of the same type on the start map.
Our assumptions hold if the goal map has been produced 
with an automatic method for area aggregation, 
for example, by the method of \citet{HaunertWolff2010AreaAgg}.
That method produces a land-cover map at a single smaller scale, 
given a land-cover map at a larger scale.
Although \textcite{HaunertWolff2010AreaAgg}
attain results of high quality, 
they do not produce a sequence land-cover maps.

In this paper, we try to find an optimal sequence
to aggregate the land-cover areas on the start map
one by one until we arrive the goal map.
We first independently deal with each region of the goal map 
(with its components on the start map).
Once we have found an aggregation sequence for each region, 
we integrate all the sequences into an overall sequence,
which transforms the start map into the goal map
(see \fig\ref{fig:AreaAgg_IntegrateSequence}). 
Our aggregation sequence may be cooperated with
the GAP-face tree \citep{vanOosterom2005},
the map cube model \citep{Timpf1998},
or ScaleMaster \citep{Brewer2007Guidelines,Touya2013ScaleMaster}, 
to support on-the-fly visualization.
Smoothly (dis-)appearing areas can be realized
by integrating our results into the \emph{space-scale cube}
\parencite{vanOosterom2014tGAP,vanOosterom2014tGAPSSC}.

@@

Map generalization generally specifies 
and takes into account requirements
in order to produce maps of high quality
\parencite{Stoter2009Requirements}.
We categorize requirements as hard and soft constraints.
For example, when users zoom out, 
some land-cover areas become too small to be seen.
These areas need to be aggregated.
When we aggregate one area into another, 
the type of the former is changed to the type of the latter. 
In this problem, a hard constraint could be that 
we aggregate only two polygons at each step 
in order to keep changes small
(see for example \fig\ref{fig:AreaAgg_example}). 
A soft constraint could be that 
we wish to minimize the changes of types, e.g., 
we prefer aggregating a grass area into a farm area 
rather than into a settlement area.
This is a typical \emph{optimization} problem,
where we stick to hard constraints and 
try to fulfill soft ones as well as possible.
Optimization for map generalization is important 
not only because it finds optimal solutions,
but also because it helps us to evaluate the quality of a model
\parencite{Haunert2017Label,
Haunert2008Assuring,Haunert2016Optimization}.
Recall that we wish to minimize the changes of types
when aggregating areas one by one.
A model could be to minimize 
the \emph{greatest} change over all the steps.
Using optimization, we are able to find optimal solutions
of this model at least for small instances.
If even the optimal solutions are bad,
then the model may be not reasonable.
In this case, we should improve the model; 
we may want to minimize 
the \emph{average} change over all the steps.
Moreover, optimization is useful for evaluating heuristics.
We need heuristics because
many optimization problems cannot be solved efficiently
\parencite[e.g.,][]{HaunertWolff2010AreaAgg,Haunert2016Partition}.
While heuristics can find some solutions in reasonable time,
it is important to know the quality of 
these solutions.
Fortunately, we can often find an optimal solution when 
the size of an instance is sufficiently small.
Consequently, we are able to evaluate 
the quality of a heuristic 
by comparing its results with optimal solutions
on small instances.

@@

To find a sequence of small changes 
that transforms the start map into the goal map,
we require that 
every change involves only two areas of the current map.
More precisely, in each step the smallest area~$u$ is merged 
with one of its neighbors~$v$ 
($v$ does not have to be the smallest neighbor)
such that~$u$ and~$v$ are replaced by their union.
The type of the union is restricted to be 
the type of either~$u$ or~$v$.
If the union uses the type of~$u$, 
we say that area~$v$ is \emph{aggregated into} area~$u$, 
and vice versa. 
How to aggregate exactly is decided by 
optimizing a global cost function.
This requirement ensures that the 
size of the smallest area on the map increases in each step.
Hence, the sequence reflects a gradual reduction of the 
map's scale.
From another perspective, 
we consider the smallest area as the least important, 
rather than involving more rules for (non-)importance. 
Even though the requirement reduces 
the number of possible solutions,
there is still enough room for optimization 
since we leave open with
which of its neighbors the smallest area is aggregated.
We term a sequence of changes 
that adheres to our smallest-first requirement simply 
an \emph{aggregation sequence}.

@@

We represent each land-cover area by a polygon with a type.
We denote by~$P$ the set of polygons on the start map.
We use~$p$, $q$, $r$, or~$o$ to denote polygons.
A \emph{patch} is a set of polygons whose union is connected. 
Each patch also has a unique land-cover area type.
We use~$u$ or~$v$ to denote the patches.

@@

\subsection{Exponential lower bound}
\label{sec:AreaAgg_Exponential}
We now analyze the size of subdivision graph~$G_\mathrm{S}$.
Our analysis is inspired by \textcite{Keane1975Size},
where we use a row of~$n$ land-cover areas.
In our instance
(see \fig\ref{fig:AreaAgg_ExponentialSize}), 
the start map consists of~$n=2k+1$ rectangular patches,
and the goal map is simply the union of the~$n$ patches.
The patches have area 
sizes~$
%\left( 
100 + \frac{1}{n}, 99+ \frac{2}{n}, 
100 + \frac{3}{n}, 99+ \frac{4}{n}, \ldots, 
99 + \frac{n-1}{n}, \text{and~} 101 
%\right)
$, 
from left to right.
According to our rule, we always 
aggregate the smallest patch with one of its neighbors.
Therefore, in the first~$k$ steps from the start map,
we aggregate every other patch with one of its neighbors.
At each of the steps, we have two choices,
aggregating with the left patch or with the right one.
As a result, there are~$2^k = 2^{(n-1)/2}$ subdivisions 
in layer~$L_{k+1}$.
That is to say, the size of subdivision graph~$G_\mathrm{S}$
has exponential lower bound.

@@

In directed acyclic graphs, shortest paths can be found slightly faster 
than in general directed or undirected graphs.
An off-the-shelf shortest-path algorithm for directed acyclic graphs
(e.g., \textcite[\sect25.2]{Cormen2009}),
however, will explore the whole graph, which has exponential size.
The challenge in our work was to tune the A* algorithm such that it
explores only a small fraction of the graph.

@@

It is difficult to define what \emph{reasonable} exactly means 
because users may have different preferences.
Four preferences have been discussed by
\textcite{Cheng2006}; see \fig\ref{fig:AreaAgg_Preferences}.
A small land-cover area can be aggregated into another area 
that isolates the area 
(\fig\ref{fig:AreaAgg_Preferences}b), 
that is the largest neighbor 
(\fig\ref{fig:AreaAgg_Preferences}c), 
that shares the longest boundary 
(\fig\ref{fig:AreaAgg_Preferences}d), or 
that has the most similar type
(\fig\ref{fig:AreaAgg_Preferences}e).
To keep our aggregation problem independent of user preferences,
our cost function takes two aspects into account: 
one based on semantics and 
the other based on shape.
%
In terms of semantics, we require that 
the \emph{type} of a land-cover area changes 
as little as possible.
This requirement means that we prefer, for example, 
aggregating an area with type \emph{swamp} 
into an area with type \emph{wet ground} 
rather than into an area with type \emph{city}.
%
In terms of shape, we hope to have areas 
which are as \emph{compact} as possible.
Our argument is that an area is easier 
to be identified by a human being 
if it is more compact (less clutter).
In this paper, we ignore the fact that
some features may inherently take linear forms
(e.g., rivers).
%
We also consider the total \emph{length} 
of the interior boundaries as an alternative compactness;
we consider subdivision~\Pnode 
as more compact than subdivision~$P_{t,i'}$ 
if the total length of the interior boundaries of~\Pnode 
is less than that of~$P_{t,i'}$.
We add this alternative because we want to make a comparison 
involving an ILP, 
where a \emph{linear} cost function must be used.
Note that most compactness measures
are \emph{not} linear;
for example, see \textcite{Maceachren1985,Li2013Compactness}.
Although the length of interior boundaries 
is not sufficiently precise 
to describe compactness \parencite{Young1988},
it is often used as a fair alternative
when compactness is considered in an ILP
\parencite[e.g.,][]{Minas2016,Wright1983}.
\textcite{HaunertWolff2010AreaAgg} employed 
the centroids of a set of land-cover areas.
One of their costs is the sum of the distances 
from the centroids to a \emph{reference point}.
The reference point is one of the centroids
that minimizes the sum.
The sum of the distances can be computed linearly.
We use the length of interior boundaries 
instead of the distance of centroids because the former 
is more relevant to the shapes of the patches.
Also, \textcite{Harrie2015Readability} showed that
longer lines generally yield lower map readability.

\begin{figure}[tb]
\centering
\includegraphics[page=1]{AreaAgg_CostsAndEstimations}
\caption{Aggregating land-cover areas 
	according to different preferences.
	Aggregating a small land-cover area into another one 
	that isolates the area (b), 
	that is the largest neighbor (c), 
	that shares the longest boundary (d), or 
	that has the most similar type (e).}
\label{fig:AreaAgg_Preferences}	
\end{figure}

@@

Suppose that we are at the step of aggregating 
from subdivision~$P_{s,i}$ to subdivision~$P_{s+1,j}$. 
In this step, patch~$u$ is aggregated into patch~$v$
(see \figs\ref{fig:AreaAgg_FirstStep}a 
and \ref{fig:AreaAgg_FirstStep}b).
We denote the types of the two patches by~$T(u)$ and~$T(v)$. 
We define the cost of type change of this step by
\begin{equation}
\label{eq:f_type}
f_\mathrm{type}(P_{s,i},P_{s+1,j})=\frac{A_{u}}{A_R}
\cdot
\frac{d(T(u),T(v))}{T_{\max}},
\end{equation}
where~$A_u$ is the area of patch~$u$, 
and~$A_R$ is the area of region~$R$
(see \sect\ref{sec:AreaAgg_Preliminaries}).
We use~$A_R$ and~$T_{\max}$ 
to normalize the cost of type change. 
Constant~$T_{\max}$, the maximum cost over all type changes,  
is known from the input. 
The input specifies, for each pair~$(T_1,T_2)$ of types, 
cost~$d(T_1,T_2)$ of changing type~$T_1$ to type~$T_2$.
Specifically, we denote by~$T_\mathrm{goal}$ the type of 
the patch on the goal map.
For simplicity, we use a metric 
as the cost function of type change
(see \sect\ref{sec:AreaAgg_CaseStudy}); 
\textcite[\chap2]{Choudhary1992Elements}
shows the definition of a metric.
A metric distance is symmetric, 
which is different from the asymmetric one used in
\textcite{Dilo2009tGAP}.
In their definition, for example, 
the distance from type \emph{building} to type \emph{road} is~$0.5$,
but the distance from \emph{road} to \emph{building} is~$0$.

@@

\begin{figure}[h]
\centering
\includegraphics[page=1]{AreaAgg_NPHard}
\caption{The reduction for our NP-hardness proof.
    The dashed polygon in (c) shows 
    that the vertices are merged.}
\label{fig:AreaAgg_Reduction}
\end{figure}

@@

\begin{figure}[h]
\centering
\includegraphics[page=2]{AreaAgg_NPHard}
\caption{The situation after Phase I has been conducted 
    such that all black vertices corresponding to a vertex cover 
    of~$G_\mathrm{A}$ have been recolored white.
    The dashed polygons show that the vertices are merged.}
\label{fig:reduction2}
\end{figure}
\end{proof}

@@

At any time~$t$,
our greedy algorithm aggregates the smallest patch
with one of its neighbors.
We pick the neighbor in a greedy way.
We suppose that the smallest patch,~$u$, has~$k_u$ neighbors,
then there are~$2k_u$ ways to aggregate
(when we aggregate a patch into another patch,
the union uses the type of the latter).
In order to guarantee that our final result
(e.g., the polygon of layer~$L_4$ in 
\fig\ref{fig:AreaAgg_SubdivisionName})
will have the type of~$T_\mathrm{goal}$,
we add one more rule to our greedy algorithm.
Suppose that patch~$v$ is one of~$u$'s neighbors.
The greedy algorithm aggregates~$u$ into~$v$ 
if the type distances fulfill that
$d\left(T(u), T_\mathrm{goal}\right) 
\ge d\left(T(v), T_\mathrm{goal}\right)$;
otherwise, the algorithm aggregates~$v$ into~$u$.
This rule excludes, say,~$k_e$ aggregation choices,
and we have~$2k_u - k_e$ choices left.
Then we compute the costs for each of 
the~$2k_u - k_e$ aggregation choices
and select the aggregation that has the least cost.
In other words, we aggregate the smallest patch with 
its most \emph{compatible} neighbor.

@@

\begin{figure*}[htb]
\centering
\includegraphics[page=5]{AreaAgg_CostsAndEstimations}
\caption{An "aggregation sequence" for computing 
	the estimated cost of length~$h_\mathrm{lgth}$ 
	(see \eqs\ref{eq:h_length} and~\ref{eq:o_length}),
	based on the lengths of interior boundaries. 
	At each step, we keep the necessary number 
	of interior boundaries with least lengths in order to find a 
	lower bound of the total length of the interior boundaries, 
	i.e., $l_\mathrm{int}(P_{s,i'''_s})$.
	The numbers represent the 
	lengths of the interior boundaries.
    Note that this aggregation sequence is impossible in reality,
    but it is fine for estimating
    (see the argument in \sect\ref{sec:AreaAgg_h_type}).    
	This example corresponds to the aggregation step in 
	\fig\ref{fig:AreaAgg_FirstStep}b.
}
\label{fig:AreaAgg_h_length}
\end{figure*}

@@

\begin{figure}[tb]
\centering
\includegraphics[page=1]{AreaAgg_CaseStudy1}
\caption{Aggregation sequences of region~$85$ 
	obtained by \Astar and the greedy algorithm.
	In order to save space, we did not show the results 
	when there are~$4$ or~$5$ patches, 
	which one can easily deduce.
	The numbers indicate the numbers of patches.
    %
    In the sequence obtained by \Astar, 
    the type of the largest polygon on the start map 
    changed only once, which is good; 
    while the type of the largest polygon changed twice 
    in the sequence obtained by the Greedy algorithm.}
\label{fig:AreaAgg_CaseStudy1_Rg85}
\end{figure}

@@

@@

>>>>

\begin{document}
\title
[Finding Optimal Sequences for Area Aggregation] %short title
{Finding Optimal Sequences for Area Aggregation---\texorpdfstring
    {\protect\\ \Astar vs.\ Integer Linear Programming} %title of the paper
    {A* vs.\ Integer Linear Programming} %title of the pdf
}

%\titlenote{Produces the permission block, and
%  copyright information}
%\subtitle{Extended Abstract}
%\subtitlenote{The full version of the author's guide is available as
%  \texttt{acmart.pdf} document}

@@

In our digital age, people interactively read maps 
on computers and mobile phones.
An often used interaction is zooming. 
When users zoom in or out, 
a map must be changed to provide information 
appropriate to the corresponding zoom level.
However, large discrete changes may distract users.
The \emph{on-the-fly generalization}~\parencite{Weibel2017Fly},
which generalizes features in real time, can mitigate this problem.
Still, large discrete changes can be introduced.
By a usability test, \textcite{Midtbo2007} have shown that 
a map is easier to follow 
if the map extent transits smoothly than stepwise. 
In addition to smoothly transiting map extent, 
we want to change also map features smoothly 
when users are zooming.
we believe that this strategy will allow users 
to follow maps even more easily.
The process of producing maps at any different scales
with smooth changes 
is known as \emph{continuous map generalization} (CMG), 
or simply \emph{continuous generalization}.
Ideally, there should be no discrete change in CMG.
However, the term is also used when 
the discrete changes are small enough not to be noticed as,
e.g., \textcite{Suba2016Road} state.
We believe that digital maps will eventually 
achieve smooth changes for zooming.
A simple way is to fade in and fade out raster maps
as did by \textcite{Pantazis2009b}.
However, we would like to carry out the changes in a more elegant way;
we would like to change map features gradually.

\mypar{Problem definition}
In this paper, we deal with CMG of land-cover areas.
The land-cover area is of significant importance on maps.
When users zoom out, some land-cover areas become
too tiny to be seen, which result in visual clutter.
In order to provide users 
with good visual experience during zooming operations,
we propose to remove these tiny areas.
We plan to achieve this goal by 
aggregating them into neighboring land-cover areas.

A \emph{land-cover map} is a planar subdivision in which 
each area belongs to a land-cover class or \emph{type}.
Suppose that there are two land-cover maps of different scales 
that cover the same spatial region.
We consider the problem of finding a sequence 
of small incremental changes that gradually transforms 
the larger-scale map (the \emph{start map}) to 
the smaller-scale map (the \emph{goal map}).
We use this sequence to generate and show land-cover maps at 
intermediate scales (see \fig\ref{fig:AreaAgg_example}).
In this way, we try to avoid large and discrete changes
during zooming.

@@

We assume that there exist many-to-one relationships 
between the areas of the start map and the areas of the goal map.
This assumption is based on the fact that many algorithms 
\parencite[e.g.,][]{HaunertWolff2010AreaAgg,
vanSmaalen2003,Oehrlein2017Aggregation}
result in many-to-one relationships
when aggregating land-cover areas.
Their inputs and generalized results together
can be used as our inputs.
However, we should not use those algorithms
to generate a sequence of maps at different scales
because those algorithms do not take into account 
the consistence between the generated maps.
We use both a start map and a goal map instead of using only the start map
because our generated maps at intermediate scales should be able to
benefit from a goal map with high quality.
We term the areas of the goal map \emph{regions}.
That is, every region is the union of a set of areas 
on the start map.
The type of a region may differ from the types of its components. 
For example, a small water area together with 
multiple adjacent forest areas may constitute 
a large forest region on the smaller-scale map.
However, we assume that every region, on the goal map, 
contains at least one area of the same type on the start map.
Our assumptions hold if the goal map has been produced 
with an automatic method for area aggregation, 
for example, by the method of \citet{HaunertWolff2010AreaAgg}.
That method produces a land-cover map at a single smaller scale, 
given a land-cover map at a larger scale.
Although \textcite{HaunertWolff2010AreaAgg}
attain results of high quality, 
they do not produce a sequence land-cover maps.

In this paper, we try to find an optimal sequence
to aggregate the land-cover areas on the start map
one by one until we arrive at the goal map.
We first independently deal with each region of the goal map 
(with its components on the start map).
Once we have found an aggregation sequence for each region, 
we integrate all the sequences into an overall sequence,
which transforms the start map into the goal map
(see \fig\ref{fig:AreaAgg_IntegrateSequence}). 
Our aggregation sequence may be cooperated with
the GAP-face tree \citep{vanOosterom2005},
the map cube model \citep{Timpf1998},
or ScaleMaster \citep{Brewer2007Guidelines,Touya2013ScaleMaster}, 
to support on-the-fly visualization.
Smoothly (dis-)appearing areas can be realized
by integrating our results into the \emph{space-scale cube}
\parencite{vanOosterom2014tGAP,vanOosterom2014tGAPSSC}.

@@

Map generalization generally specifies 
and takes into account requirements
in order to produce maps of high quality
\parencite{Stoter2009Requirements}.
We categorize requirements as hard and soft constraints.
For example, when users zoom out, 
some land-cover areas become too small to be seen.
These areas need to be aggregated.
When we aggregate one area into another, 
the type of the former is changed to the type of the latter. 
In this problem, a hard constraint could be that 
we aggregate only two polygons at each step 
in order to keep changes small
(see for example \fig\ref{fig:AreaAgg_example}). 
A soft constraint could be that 
we wish to minimize the changes of types, e.g., 
we prefer aggregating a grass area into a farm area 
rather than into a settlement area.
This is a typical \emph{optimization} problem,
where we stick to hard constraints and 
try to fulfill soft ones as well as possible.
Optimization for map generalization is important 
not only because it finds optimal solutions,
but also because it helps us to evaluate the quality of a model
\parencite{Haunert2017Label,
Haunert2008Assuring,Haunert2016Optimization}.
When we wish to minimize the changes of types
in aggregating areas one by one,
a model could be to minimize 
the \emph{greatest} change over all the steps.
Using a greedy algorithm,
we can minimize the change at each step,
but the result does not necessarily minimize the greatest change
over all the steps.
If a result is bad,
we cannot tell if the bad result comes from the model 
or from the greedy algorithm.
Using optimization,
we are able to find optimal solutions
of the model at least for small instances.
If even an optimal solution is bad,
then we can exclude that the bad result 
is from the greedy algorithm.
That is to say,
the bad result is because of the model.
In this case, we should improve the model; 
we may want to minimize 
the \emph{average} change over all the steps.
Moreover, optimization is useful for evaluating heuristics.
We need heuristics because
many optimization problems cannot be solved efficiently
\parencite[e.g.,][]{HaunertWolff2010AreaAgg,Haunert2016Partition}.
While heuristics can find some solutions in reasonable time,
it is important to know the quality of 
these solutions.
Fortunately, we can often find an optimal solution when 
the size of an instance is sufficiently small.
Consequently, we are able to evaluate 
the quality of a heuristic 
by comparing its results with optimal solutions
on small instances.

@@

To find a sequence of small changes 
that transforms the start map into the goal map,
we require that 
every change involves only two areas of the current map.
More precisely, in each step the smallest area~$u$ is merged 
with one of its neighbors~$v$ 
($v$ does not have to be the smallest neighbor)
such that~$u$ and~$v$ are replaced by their union.
The type of the union is restricted to be 
the type of either~$u$ or~$v$.
If the union uses the type of~$u$, 
we say that area~$v$ is \emph{aggregated into} area~$u$, 
and vice versa. 
How to aggregate exactly is decided by 
optimizing a global cost function
(see \sect\ref{sec:AreaAgg_CostFunctions}).
This requirement ensures that the 
size of the smallest area on the map increases in each step.
Hence, the sequence reflects a gradual reduction of the 
map's scale.
From another perspective, 
we consider the smallest area as the least important, 
rather than involving more rules for (non-)importance. 
Even though the requirement reduces 
the number of possible solutions,
there is still enough room for optimization 
since we leave open with
which of its neighbors the smallest area is aggregated.
We term a sequence of changes 
that adheres to our smallest-first requirement simply 
an \emph{aggregation sequence}.

@@

We represent each land-cover area by a polygon with a type.
We denote by~$P$ the set of polygons on the start map.
We use~$p$, $q$, $r$, or~$o$ to denote polygons.
A \emph{patch} is a set of polygons whose union is connected. 
Each patch also has a unique land-cover type.
We use~$u$ or~$v$ to denote the patches.

@@

\subsection{Exponential lower bound}
\label{sec:AreaAgg_Exponential}
We now analyze the size of subdivision graph~$G_\mathrm{S}$.
Our analysis is inspired by \textcite{Keane1975Size},
where we use a row of~$n$ land-cover areas.
In our instance
(see \fig\ref{fig:AreaAgg_ExponentialSize}), 
the start map consists of~$n=2k+1$ rectangular patches,
and the goal map is simply the union of the~$n$ patches.
The patches have area 
sizes~$
%\left( 
100 + \frac{1}{n}, 99+ \frac{2}{n}, 
100 + \frac{3}{n}, 99+ \frac{4}{n}, \ldots, 
99 + \frac{n-1}{n}, \text{and~} 101 
%\right)
$, 
from left to right.
According to our rule, we always 
aggregate the smallest patch with one of its neighbors.
Therefore, in the first~$k$ steps from the start map,
we aggregate every other patch with one of its neighbors.
However, we do not know which one is the right choice
at each of the steps,
in order to minimize our costs (see \sect\ref{sec:AreaAgg_CostFunctions}).
We have to try both of the two choices,
aggregating with the left patch or with the right one.
As a result, there are~$2^k = 2^{(n-1)/2}$ subdivisions 
in layer~$L_{k+1}$.
That is to say, the size of subdivision graph~$G_\mathrm{S}$
has exponential lower bound.

@@

In directed acyclic graphs, shortest paths can be found slightly faster 
than in general directed or undirected graphs.
An off-the-shelf shortest-path algorithm for directed acyclic graphs
%\parencite[e.g.,][\sect25.2]{Cormen2009},
(e.g., \textcite[\sect25.2]{Cormen2009}),
however, will explore the whole graph, which has exponential size.
The challenge in our work was to tune the A* algorithm such that it
explores only a small fraction of the graph.

@@

It is difficult to define what \emph{reasonable} exactly means 
because users may have different preferences.
Four preferences have been discussed by
\textcite{Cheng2006}; see \fig\ref{fig:AreaAgg_Preferences}.
A small land-cover area can be aggregated into another area 
that isolates the area 
(\fig\ref{fig:AreaAgg_Preferences}b), 
that is the largest neighbor 
(\fig\ref{fig:AreaAgg_Preferences}c), 
that shares the longest boundary 
(\fig\ref{fig:AreaAgg_Preferences}d), or 
that has the most similar type
(\fig\ref{fig:AreaAgg_Preferences}e).
To keep our aggregation problem independent of user preferences,
our cost function takes two aspects into account: 
one based on semantics and 
the other based on shape.
%
In terms of semantics, we require that 
the \emph{type} of a land-cover area changes 
as little as possible.
This requirement means that we prefer, for example, 
aggregating an area with type \emph{swamp} 
into an area with type \emph{wet ground} 
rather than into an area with type \emph{city}.
%
In terms of shape, we hope to have areas 
which are as \emph{compact} as possible.
Our argument is that an area is easier 
to be identified by a human being 
if it is more compact (less clutter).
%
We also consider the total \emph{length} 
of the interior boundaries as an alternative compactness;
we consider subdivision~\Pnode 
as more compact than subdivision~$P_{t,i'}$ 
if the total length of the interior boundaries of~\Pnode 
is less than that of~$P_{t,i'}$.
We add this alternative because we want to make a comparison 
involving an ILP, 
where a \emph{linear} cost function must be used.
Note that most compactness measures
are \emph{not} linear;
for example, see \textcite{Maceachren1985,Li2013Compactness}.
Although the length of interior boundaries 
is not sufficiently precise 
to describe compactness \parencite{Young1988},
it is often used as a fair alternative
when compactness is considered in an ILP
\parencite[e.g.,][]{Minas2016,Wright1983}.
\textcite{HaunertWolff2010AreaAgg} employed 
the centroids of a set of land-cover areas.
One of their costs is the sum of the distances 
from the centroids to a \emph{reference point}.
The reference point is one of the centroids
that minimizes the sum.
The sum of the distances can be computed linearly.
We use the length of interior boundaries 
instead of the distance of centroids because the former 
is more relevant to the shapes of the patches.
Also, \textcite{Harrie2015Readability} showed that
longer lines generally yield lower map readability.

\begin{figure}[tb]
\centering
\includegraphics[page=1]{AreaAgg_CostsAndEstimations}
\caption{Aggregating land-cover areas 
	according to different preferences
    by \textcite{Cheng2006}.
	Aggregating a small land-cover area into another one 
	that isolates the area (b), 
	that is the largest neighbor (c), 
	that shares the longest boundary (d), or 
	that has the most similar type (e).}
\label{fig:AreaAgg_Preferences}	
\end{figure}

@@

Suppose that we are at the step of aggregating 
from subdivision~$P_{s,i}$ to subdivision~$P_{s+1,j}$. 
In this step, patch~$u$ is aggregated into patch~$v$
(see \figs\ref{fig:AreaAgg_FirstStep}a 
and \ref{fig:AreaAgg_FirstStep}b).
We denote the types of the two patches by~$T(u)$ and~$T(v)$. 
We define the cost of type change of this step by
\begin{equation}
\label{eq:f_type}
f_\mathrm{type}(P_{s,i},P_{s+1,j})=\frac{A_{u}}{A_R}
\cdot
\frac{d_\mathrm{type}(T(u),T(v))}{d_\mathrm{type\_max}},
\end{equation}
where~$A_u$ is the area of patch~$u$, 
and~$A_R$ is the area of region~$R$
(see \sect\ref{sec:AreaAgg_Preliminaries}).
We use~$A_R$ and~$d_\mathrm{type\_max}$ 
to normalize the cost of type change. 
Constant~$d_\mathrm{type\_max}$, the maximum cost over all type changes,  
is known from the input. 
The input specifies, for each pair~$(T_1,T_2)$ of types, 
cost~$d_\mathrm{type}(T_1,T_2)$ of changing type~$T_1$ to type~$T_2$.
Specifically, we denote by~$T_\mathrm{goal}$ the type of 
the patch on the goal map.
For simplicity, we use a metric 
as the cost function of type change
(see \sect\ref{sec:AreaAgg_CaseStudy}); 
\textcite[\chap2]{Choudhary1992Elements}
shows the definition of a metric.
A metric distance is symmetric, 
which is different from the asymmetric one used in
\textcite{Dilo2009tGAP}.
In their definition, for example, 
the distance from type \emph{building} to type \emph{road} is~$0.5$,
but the distance from \emph{road} to \emph{building} is~$0$.

@@

\begin{figure}[tb]
\centering
\includegraphics[page=1]{AreaAgg_NPHard}
\caption{The reduction for our NP-hardness proof.
    The dashed polygon in (c) shows 
    that the vertices are merged.}
\label{fig:AreaAgg_Reduction}
\end{figure}

@@

\begin{figure}[tb]
\centering
\includegraphics[page=2]{AreaAgg_NPHard}
\caption{The situation after Phase I has been conducted 
    such that all black vertices corresponding to a vertex cover 
    of~$G_\mathrm{A}$ have been recolored white.
    The dashed polygons show that the vertices are merged.}
\label{fig:reduction2}
\end{figure}
\end{proof}

@@

At any time~$t$,
our greedy algorithm aggregates the smallest patch
with one of its neighbors.
We pick the neighbor in a greedy way.
We suppose that the smallest patch,~$u$, has~$k_u$ neighbors,
then there are~$2k_u$ ways to aggregate
(when we aggregate a patch into another patch,
the union uses the type of the latter).
In order to guarantee that our final result
(e.g., the polygon of layer~$L_4$ in 
\fig\ref{fig:AreaAgg_SubdivisionName})
will have the type of~$T_\mathrm{goal}$,
we add one more rule to our greedy algorithm.
Suppose that patch~$v$ is one of~$u$'s neighbors.
The greedy algorithm aggregates~$u$ into~$v$ 
if the type distances fulfill that
$d_\mathrm{type}\left(T(u), T_\mathrm{goal}\right) 
\ge d_\mathrm{type}\left(T(v), T_\mathrm{goal}\right)$;
otherwise, the algorithm aggregates~$v$ into~$u$.
This rule excludes, say,~$k_e$ aggregation choices,
and we have~$2k_u - k_e$ choices left.
Then we compute the costs for each of 
the~$2k_u - k_e$ aggregation choices
and select the aggregation that has the least cost.
In other words, we aggregate the smallest patch with 
its most \emph{compatible} neighbor.

@@

\begin{figure*}[tb]
\centering
\includegraphics[page=5]{AreaAgg_CostsAndEstimations}
\caption{An "aggregation sequence" for computing 
	the estimated cost of length~$h_\mathrm{lgth}$ 
	(see \eqs\ref{eq:h_length} and~\ref{eq:o_length}),
	based on the lengths of interior boundaries. 
	At each step, we keep the necessary number 
	of interior boundaries with least lengths in order to find a 
	lower bound of the total length of the interior boundaries, 
	i.e., $\ell_\mathrm{int}(P_{s,i'''_s})$.
	The numbers represent the 
	lengths of the interior boundaries.
    Note that this aggregation sequence is impossible in reality,
    but it is fine for estimating
    (see the argument in \sect\ref{sec:AreaAgg_h_type}).    
	This example corresponds to the aggregation step in 
	\fig\ref{fig:AreaAgg_FirstStep}b.
}
\label{fig:AreaAgg_h_length}
\end{figure*}

@@

\begin{figure}[tb]
\centering
\includegraphics[page=1]{AreaAgg_CaseStudy1}
\caption{Aggregation sequences of region~$85$ 
	obtained by \Astar and the greedy algorithm.
	In order to save space, we did not show the results 
	when there are~$4$ or~$5$ patches, 
	which one can easily deduce.
	The numbers indicate the numbers of patches.
    %
    In the sequence obtained by \Astar, 
    the type of the largest polygon on the start map 
    changed only once, which is good; 
    while the type of the largest polygon changed twice 
    in the sequence obtained by the greedy algorithm.}
\label{fig:AreaAgg_CaseStudy1_Rg85}
\end{figure}

@@

\clearpage

@@

%\clearpage
